TGI Spinal Analysis Code

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
all data plot

# Let's look at the data!
```{r}
# Reorganise data-frame 
# pivot longer the VAS response by each quality of sensation
# do this for both RT and VAS
df_long <-

# then remove NaNs for burning

# then plot :D
```

>>>>

# Let's look at the data!
```{r}
# Reorganise data-frame 
# pivot longer the VAS response by each quality of sensation
# do this for both RT and VAS
df_long <- df_res %>% 
  pivot_longer(cols = c(VASinit, VASburn, VASwarm, VAScold),
               names_to = 'quality',
               values_to = 'VAS')
df_long2 <- df_res %>% 
  pivot_longer(cols = c(RTinit, RTburn, RTwarm, RTcold),
               names_to = 'quality',
               values_to = 'RT')
# remove the VAS & RT from quality column
df_long$quality <- substr(df_long$quality, 4, 7)
df_long2$quality <- substr(df_long2$quality, 3, 6)
# remove columns from both then merge
df_long <- df_long[, c(1:12,17:19)]
df_long2 <- df_long2[, c(1:12,17:19)]
df_long <- merge(df_long, df_long2)

# then remove NaNs
df_long <- df_long %>% filter(!is.na(VAS))
# remove the initial trials - not important for now
init_burn <- filter(df_long, quality == 'init')
all_vas <- filter(df_long, quality != 'init')

# calculate means
vas_meds <- aggregate(VAS ~ quality*manipulation*cold_probe*ID, median, data = all_vas)
# then plot :D
blue <- brewer.pal(6, "Blues")
grey <- brewer.pal(6, "Greys")

ggplot(vas_meds, aes(cold_probe, VAS, colour = manipulation, group = ID)) +
  geom_point(position = position_dodge(.2)) +
  facet_wrap(~quality) +
  scale_colour_manual(values = c(grey[3], blue[4])) +
  theme_bw()
```
